Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
small change

For each province, we take a 7 day rolling sum on the number of new cases each day, and feed the data into the parametric SI model, which is given distribution $w(\tau)$ From there, the model uses a likelihood based approach to estiamte R at each discrete timestep, computing the likelihood that a person at timestep $i$ is infected by a person infected at timestep $j$, and summing the likelihood for each $j$ across all its infectees to compute the $R$ value at timestep $j$. Thus, for each province, we produce a daily time series estimate for $R$ on each day. This method is outlined in detail in Wallinga and Teunis (2004)[8].

@@

$$ \beta^T = [-0.23198507 -0.05391226  0.26336295 -0.03586852] $$

@@

With our `cfc19i` library, it is

>>>>

For each province, we take a 7 day rolling sum on the number of new cases each day, and feed the data into the parametric SI model, which is given distribution $w(\tau)$ based on the SI parameters. From there, the model uses a likelihood based approach to estiamte R at each discrete timestep, computing the likelihood that a person at timestep $i$ is infected by a person infected at timestep $j$, and summing the likelihood for each $j$ across all its infectees to compute the $R$ value at timestep $j$. Thus, for each province, we produce a daily time series estimate for $R$ on each day. This method is outlined in detail in Wallinga and Teunis (2004)[8].

@@

$$ \beta^T = [-0.23198507, -0.05391226, 0.26336295, -0.03586852] $$

@@
